Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-29 paper/ms.tex
update manuscript

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals, and the errorbar shows the median uncertainty for the
    black points.  The gray line shows the median model corresponding
    to the combined TESS and ground-based transit fit.
    (Table~2).  {\it Bottom:} Multicolor photometry from the El Sauce
    0.36m; gray points are binned to 10-minute intervals.  Models show
    lower limits on the transit depths in the Cousins-R and Johnson-B
    bandpasses used to rule out specific false positive scenarios.
    \label{fig:jointphot}
	}
\end{figure*}

@@

\subsubsection{Multicolor Photometry}
% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
% at most.

@@

For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.38$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
limit is 0.82$M_\odot$.

>>>>

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals, and the errorbar shows the median uncertainty for the
    black points.  The gray line shows the median model corresponding
    to the combined TESS and ground-based transit fit
    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
    0.36m; gray points are binned to 10-minute intervals.  Models show
    $2\sigma$ lower limits on the transit depths in the Cousins-R and
    Johnson-B bandpasses used to rule out specific false positive
    scenarios (see Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

\subsubsection{Multicolor Photometry}
\label{subsec:colorphot}
% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
% at most.

@@

%FIXME FIXME
For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.38$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
limit is 0.82$M_\odot$.
